Paper 1 Analysis

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
delta_1 = 0.5?

<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
PTkleresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
any(PTkleresample$delta_1 >= 1)
1 - max(PTkleresample$delta_1)
PTklerange95 <- quantile(PTkleresample$delta_1, probs=c(0.025, 0.975))
PTklerange95
1 - PTklerange95
@

>>>>

<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
PTkleresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
any(PTkleresample$delta_1 >= 1)
1 - max(PTkleresample$delta_1)
PTklerange95 <- quantile(PTkleresample$delta_1, probs=c(0.025, 0.975))
PTklerange95
1 - PTklerange95
# See if there are any coefficients that are exactly 0.5, the starting value.
any(resampleCoeffsCES$delta_1 == 0.5)
@
